Oregon_Wildfire_reduced

### 2017-02-22 r_scripts/oregon_clean.rmd
Update oregon_clean.rmd
make categories and make table, check dates

## 1. Personkey ?? not shown?
```{r}
personkey2 <- oregon_df %>% 
  select(personkey) %>%
  mutate(personkey_cat = ifelse(!is.na(personkey), "Non-Missing", 
                         ifelse(is.na(personkey), "Missing", NA))) %>% 
  group_by(personkey_cat) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
         percent = round(n/total_n, 4)*100) %>%
      select(personkey_cat, n, percent)

# table ----
knitr::kable(personkey2, caption = "Patient ID")

@@

## 2. Patid ???
```{r}
patid2 <- oregon_df %>% 
  select(patid) %>%
  mutate(patid_cat = ifelse(!is.na(patid), "Non-Missing", 
                         ifelse(is.na(patid), "Missing", NA))) %>% 
  group_by(patid_cat) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
         percent = round(n/total_n, 4)*100) %>%
      select(patid_cat, n, percent)

@@

## State
```{r}
state2 <- oregon_df %>%
  select(STATE) %>%
  group_by(STATE) %>%
  summarise(n = n()) %>%
  mutate(total_n = sum(n),
         percent = round(n/total_n, 4)*100,
         state_cat = ifelse(STATE == "OR", "Oregon",
                     ifelse(STATE != "OR"&is.na(STATE)==F, "Not Oregon",NA))) %>%
    select(STATE, state_cat, n, percent)

@@

## ZIP
```{r}
zip2 <- oregon_df %>%
  select(ZIP) %>%
  group_by(ZIP) %>%
  summarise(n = n()) %>%
  mutate(total_n = sum(n),
         percent = round(n/total_n, 4)*100,
         zip_cat = ifelse(is.na(ZIP) == 0, "Non-Missing",
                   ifelse(is.na(ZIP) != 0, "Missing", NA))) %>%
    select(ZIP, zip_cat, n, percent)

@@

## MSA
```{r}
msa2 <- oregon_df %>%
  select(MSA) %>%
  mutate(msa_cat = ifelse(MSA != "", "Non-Missing",
                   ifelse(MSA == "", "Missing", NA))) %>% 
  group_by(msa_cat) %>%
  summarise(n = n()) %>%
  mutate(total_n = sum(n),
         percent = round(n/total_n, 4)*100) %>%
  select(msa_cat, n, percent)

@@

## Pos
```{r}
pos2 <- oregon_df %>%
  select(pos) %>%
  group_by(pos) %>%
  summarise(n = n()) %>%
  mutate(total_n = sum(n),
         percent = round(n/total_n, 4)*100,
         Place_of_service = ifelse(pos == "20", "Urgent Care Facility",
                            ifelse(pos == "23", "Emergency Room – Hospital", 
                            ifelse(is.na(pos) == 0, "Not Urgent", 
                            ifelse(is.na(pos) ==1, "Missing", NA))))) %>%
    select(pos, Place_of_service, n, percent)

@@

## from date
```{r}
fromdate2 <- oregon_df %>%
  select(fromdate) %>%
  mutate(dates = as.Date(fromdate2$fromdate, "%Y-%m-%d"))

@@

## to date
```{r}
todate2 <- oregon_df %>%
  select(todate) %>%
  mutate(ddd = as.Date(todate2$todate, "%Y-%m-%d"))

todate3 <- oregon_df %>%
  filter (todate > "2014-12-31")
todate3

which(oregon_df$todate=="2299-12-31") # 129192

@@

hist(todate2$ddd, "days", freq = TRUE)

@@

## Length of stay
```{r}

>>>>

## 1. Personkey 
```{r}
personkey2 <- oregon_df %>% 
  select(personkey) %>%
  mutate(personkey_cat = ifelse(!is.na(personkey), "Non-Missing", 
                         ifelse(is.na(personkey), "Missing", NA))) %>% 
  group_by(personkey_cat) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
         percent = round(n/total_n, 4)*100) %>%
  select(personkey_cat, n, percent)

# table ----
knitr::kable(personkey2, align = "c", caption = "Patient ID")

@@

## 2. Patid
```{r}
patid2 <- oregon_df %>% 
  select(patid) %>%
  mutate(patid_cat = ifelse(!is.na(patid), "Non-Missing", 
                         ifelse(is.na(patid), "Missing", NA))) %>% 
  group_by(patid_cat) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
         percent = round(n/total_n, 4)*100) %>%
      select(patid_cat, n, percent)

@@

## State ???
```{r}
state2 <- oregon_df %>%
  select(STATE) %>%
  group_by(STATE) %>%
  summarise(n = n()) %>%
  mutate(total_n = sum(n),
         percent = round(n/total_n, 4)*100,
         state_cat = ifelse(STATE == "", "Missing",
                     ifelse(STATE == "OR", "Oregon",
                     ifelse(STATE != "OR", "Not Oregon",NA)))) %>%
    select(STATE, state_cat, n, percent)

@@

## ZIP 
```{r}
# summary(as.factor(oregon_df$ZIP))

# which(oregon_df$ZIP == "")

zip2 <- oregon_df %>% 
  select(ZIP) %>%
  mutate(zip_cat = ifelse(ZIP == "", "Missing", 
                   ifelse(!is.na(ZIP), "Non-Missing", NA))) %>% 
  group_by(zip_cat) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
         percent = round(n/total_n, 4)*100) %>%
      select(zip_cat, n, percent)

@@

## MSA ??? missing 58
```{r}
msa2 <- oregon_df %>% 
  select(MSA) %>%
  mutate(msa_cat = ifelse(!is.na(MSA), "Non-Missing", 
                   ifelse(MSA=="     ", "Missing", NA))) %>% 
  group_by(msa_cat) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
         percent = round(n/total_n, 4)*100) %>%
      select(msa_cat, n, percent)

@@

## Pos NA: 2974
```{r}
library(readxl)
pos_key <- read_excel("../instructions/LT_pos.xlsx")
summary(pos_key)

pos2 <- oregon_df %>%
  select(pos)

which(pos2$pos=="0S") # 14553
as.numeric(pos2$pos[14553])

pos2$pos <- as.numeric(pos2$pos)

pos2 <- pos2 %>%
  group_by(pos) %>%
  summarise(n = n()) %>%
  mutate(total_n = sum(n),
         percent = round(n/total_n, 4)*100,
         Place_of_service = ifelse(pos == pos_key$Code[1], pos_key$Value[1],
                            ifelse(pos == pos_key$Code[2], pos_key$Value[2],
                            ifelse(pos == pos_key$Code[3], pos_key$Value[3],       
                            ifelse(pos == pos_key$Code[4], pos_key$Value[4],       
                            ifelse(pos == pos_key$Code[5], pos_key$Value[5],       
                            ifelse(pos == pos_key$Code[6], pos_key$Value[6],        
                            ifelse(pos == pos_key$Code[7], pos_key$Value[7],
                            ifelse(pos == pos_key$Code[8], pos_key$Value[8],     
                            ifelse(pos == pos_key$Code[9], pos_key$Value[9],      
                            ifelse(pos == pos_key$Code[10], pos_key$Value[10],      
                            ifelse(pos == pos_key$Code[11], pos_key$Value[11],      
                            ifelse(pos == pos_key$Code[12], pos_key$Value[12],    
                            ifelse(pos == pos_key$Code[13], pos_key$Value[13],     
                            ifelse(pos == pos_key$Code[14], pos_key$Value[14],        
                            ifelse(pos == pos_key$Code[15], pos_key$Value[15],      
                            ifelse(pos == pos_key$Code[16], pos_key$Value[16],     
                            ifelse(pos == pos_key$Code[17], pos_key$Value[17],      
                            ifelse(pos == pos_key$Code[18], pos_key$Value[18],     
                            ifelse(pos == pos_key$Code[19], pos_key$Value[19],      
                            ifelse(pos == pos_key$Code[20], pos_key$Value[20],       
                            ifelse(pos == pos_key$Code[21], pos_key$Value[21],     
                            ifelse(pos == pos_key$Code[22], pos_key$Value[22],      
                            ifelse(pos == pos_key$Code[23], pos_key$Value[23],      
                            ifelse(pos == pos_key$Code[24], pos_key$Value[24],      
                            ifelse(pos == pos_key$Code[25], pos_key$Value[25],     
                            ifelse(pos == pos_key$Code[26], pos_key$Value[26],      
                            ifelse(pos == pos_key$Code[27], pos_key$Value[27],      
                            ifelse(pos == pos_key$Code[28], pos_key$Value[28],      
                            ifelse(pos == pos_key$Code[29], pos_key$Value[29],      
                            ifelse(pos == pos_key$Code[30], pos_key$Value[30],     
                            ifelse(pos == pos_key$Code[31], pos_key$Value[31],     
                            ifelse(pos == pos_key$Code[32], pos_key$Value[32],      
                            ifelse(pos == pos_key$Code[33], pos_key$Value[33],
                            ifelse(pos == pos_key$Code[34], pos_key$Value[34],
                            ifelse(pos == pos_key$Code[35], pos_key$Value[35],
                            ifelse(pos == pos_key$Code[36], pos_key$Value[36],                                   
                            ifelse(pos == pos_key$Code[37], pos_key$Value[37],
                            ifelse(pos == pos_key$Code[38], pos_key$Value[38],                                   
                            ifelse(pos == pos_key$Code[39], pos_key$Value[39],                                   
                            ifelse(pos == pos_key$Code[40], pos_key$Value[40],                                   
                            ifelse(pos == pos_key$Code[41], pos_key$Value[41],                                   
                            ifelse(pos == pos_key$Code[42], pos_key$Value[42],                                   
                            ifelse(pos == pos_key$Code[43], pos_key$Value[43],                                   
                            ifelse(pos == pos_key$Code[44], pos_key$Value[44],                                  
                            ifelse(pos == pos_key$Code[45], pos_key$Value[45],                                   
                            ifelse(pos == pos_key$Code[46], pos_key$Value[46],                                   
                            ifelse(is.na(pos), "Missing", NA
                                   )))))))))))))))))))))))))))))))))))))))))))))))) %>%
    select(pos, Place_of_service, n, percent)

pos2$Place_of_service[which(is.na(pos2$pos))] <- "Missing"
pos2$pos[which(is.na(pos2$pos))] <- "Missing"

@@

## from date (All data is in 2013)
```{r}
fromdate2 <- oregon_df %>%
  select(fromdate) %>%
  mutate(dates = as.Date(fromdate, "%Y-%m-%d"))

fromdate_check <- oregon_df %>%
  filter((fromdate > "2014-12-31"| fromdate < "2013-01-01"))

@@

## to date (min: 1913-02-17; max: 2299-12-31)
```{r}
todate2 <- oregon_df %>%
  select(todate) %>%
  mutate(ddd = as.Date(todate, "%Y-%m-%d"))

todate3 <- oregon_df %>%
  filter (todate > "2014-12-31"| todate < "2013-01-01")
todate3

which(oregon_df$todate=="2299-12-31") # 129192
which(oregon_df$todate=="1913-10-25") # 178869

@@

hist(todate2$ddd[c(-129192,-178869)], "days", freq = TRUE)

@@

## Length of stay
```{r}
summary(as.factor(oregon_df$los))
